WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-03 paper/Manuscript_DS.Rmd
R1 C11: Synthetic data

The second solution is to share a synthetic dataset with similar characteristics
to the real data. Synthetic data mimic the level of measurement and
(conditional) distributions of the real data
[see @nowokSynthpopBespokeCreation2016]. Sharing synthetic data allows any third
party to 1) verify that the published code works, 2) debug the code, and 3)
write valid code for alternative analyses. It is important to note that complex
multivariate relationships present in the real data are often lost in synthetic
data. Thus, findings from the real data might not be replicated in the synthetic
data, and findings in the synthetic data *should not be substantively interpreted*.
Still, sharing synthetic data facilitates data requests from third parties. A
third party can write analysis code based on the synthetic data, and send it to
the authors who evaluate it on the real data and send back the results. The
`worcs` package offers a simple but flexible function to generate synthetic data,
`synthetic()`, which by default uses random forests to generate a model for
synthesis (see @wrightRangerFastImplementation2015).

>>>>

The second solution is to share a synthetic dataset with similar characteristics
to the real data. Synthetic data mimic the level of measurement and
(conditional) distributions of the real data
[see @nowokSynthpopBespokeCreation2016]. Sharing synthetic data allows any third
party to 1) verify that the published code works, 2) debug the code, and 3)
write valid code for alternative analyses. It is important to note that complex
multivariate relationships present in the real data are often lost in synthetic
data. Thus, findings from the real data might not be replicated in the synthetic
data, and findings in the synthetic data *should not be substantively interpreted*.
Still, sharing synthetic data facilitates data requests from third parties. A
third party can write analysis code based on the synthetic data, and send it to
the authors who evaluate it on the real data and send back the results. The
`worcs` package offers a simple but flexible function to generate synthetic data,
`synthetic()`, which by default uses random forests to generate a model for
synthesis (see @wrightRangerFastImplementation2015).
This function is based on the work by @nowokSynthpopBespokeCreation2016 (see the `R` package `synthpop`),
but with a simpler and more flexible user interface.
Specifically, the `worcs` function `synthetic()` accepts any function that can be used to model
marginal associations in the data.
For further details, see the [function documentation](https://cjvanlissa.github.io/worcs/reference/synthetic.html).

### 2020-11-03 paper/reviews_ds.Rmd
R1 C11: Synthetic data

\RC{Synthetic data generation is fantastic, but it is not clear to me how does worcs actually keep the data consistent e.g. for training models. Does it follow a similar distribution to the source data?}

Response: Provide reference, clarify explanation in text.

>>>>

\RC{C11: Synthetic data generation is fantastic, but it is not clear to me how does worcs actually keep the data consistent e.g. for training models. Does it follow a similar distribution to the source data?}

Response: We agree that synthetic data generation is exciting, but feel obliged to clarify that this is **not** a novel contribution of the present paper nor R-package. 
As indicated in the paper, we use the algorithm by Nowok and colleagues,
who explain the details of the method.
We re-implemented the method in the `worcs` package because the `synthpop` package
is rarely maintained (e.g., one of our pull requests took almost 10 months to be accepted),
and because we wanted a more flexible, customizable interface.

To answer the Reviewer's specific question, the synthetic data indeed follow similar distributions to the source data, as indicated in the paper:

> Synthetic data mimic the level of measurement and
(conditional) distributions of the real data
[see @nowokSynthpopBespokeCreation2016].

We have additionally clarified the paragraph that introduces the `synthetic()` function, and added further references to the methodological paper,
and to the documentation of the `synthetic()` function (which summarizes the algorithm).
